\documentclass[conference, 10pt]{IEEEtran}
%\setlength\columnsep{0.2in}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{amsmath,amssymb,amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\usepackage{graphicx}
%\usepackage{geometry}
%\usepackage{subfigure}
\usepackage{url}
\usepackage{multirow}
\usepackage{listings}
\usepackage{cite}
\usepackage{array}
\usepackage{enumerate}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{color}
\usepackage{soul}
%\geometry{left=0.7in,right=0.7in,top=1in,bottom=1in}

%IEEE S&P Submitted papers may include up to 13 pages of text and up to 5 pages for references and appendices, totalling no more than 18 pages.

\begin{document}
\pagenumbering{arabic}
\title{{UPRESSO}: An Unlinkable Privacy-REspecting Single Sign-On System}
%\title{{Recluse}: A Privacy-Respecting Single Sign-On System Achieving Unlinkable Users' Traces}
%\title{{Recluse}: A Privacy-Respecting Single Sign-On System Avoiding User Linkage and Tracing}
%\title{EOIDC: An Enhanced OpenID-Connect Protocol That Protect Users' Privacy}
%
% Single address.
% ---------------
%\name{Anonymous ICME submission}
%\address{}
\maketitle
\begin{abstract}
%(e.g., shifting the risks for managing the user's credentials) (e.g., reducing the number of credentials)
 The Single Sign-On (SSO) service, provided by identity provider (IdP),  is widely deployed and integrated to bring the convenience to both the relying party (RP) and the users.
% by shifting the users' credentials to the identity provider (IdP) and reducing the user's maintained  credentials.
 However, the privacy leakage is an obstacle to the users' adoption of SSO,
 as the curious IdP may track at which RPs users log in,
% as the curious IdP knows which RPs to be accessed by a user
while collusive RPs could link the user from a common or related identifer(s) issued by the IdP.
 %while the RPs may link the user with the non-independent identifiers in the identity proof provided by the IdP.
 Existing solutions preserve the user's privacy  from either the curious IdP or the collusive RPs, but never from the both entities.
In this paper, we provide an SSO system, named UPRESSO, to hide the user's accessed RPs from the curious IdP
and prevent the identity linkage from the collusive RPs.
In UPRESSO, IdP generates a different privacy-preserving ID ($PID_U$) for a user among RPs, and binds $PID_U$ with a transformation of the RP identifier ($PID_{RP}$), without obtaining the real RP identifier.
Each RP uses a trapdoor to derive the user's unique account from $PID_U$,
while a user's accounts are different among the RPs.
%based on the transformation of the RP identifiers and user's accounts on the discrete logarithm problem.
UPRESSO  is compatible with OpenID Connect, a widely deployed and well analyzed SSO system;
    where dynamic registration is utilized to make $PID_{RP}$ valid in the IdP.
    % finish xx and xx to xxx. % 利用动态注册来xx，xxx来搞定xxx；一句话的大概说明
The analysis shows that user's privacy is preserved in UPRESSO without any degradation on the security of OpenID Connect.
%Recluse is proved to preserve the user's privacy without any degradation on the security of OpenID Connect.
We have implemented a prototype of UPRESSO. The evaluation demonstrates that UPRESSO is efficient, and only needs 208 ms for a user to login at an RP in our environment.
\end{abstract}
\begin{IEEEkeywords}
Single Sign-On, security, privacy, trace, linkage
\end{IEEEkeywords}

\input{chap/introduction.tex}
\input{chap/background.tex}
\input{chap/challenges.tex}
\input{chap/threatmodel.tex}
\input{chap/protocol.tex}
\input{chap/analysis.tex}
\input{chap/implementation.tex}
\input{chap/evaluation.tex}
\input{chap/discussion.tex}
\input{chap/relatedwork.tex}
\input{chap/conclusion.tex}

\bibliographystyle{IEEEbib}
\bibliography{ref}

\end{document}
