\documentclass[conference, 10pt]{IEEEtran}
%\setlength\columnsep{0.2in}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{amsmath,amssymb,amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\usepackage{graphicx}
%\usepackage{geometry}
%\usepackage{subfigure}
\usepackage{url}
\usepackage{multirow}
\usepackage{listings}
\usepackage{cite}
\usepackage{array}
\usepackage{enumerate}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{color}
\usepackage{soul}
%\geometry{left=0.7in,right=0.7in,top=1in,bottom=1in}

%IEEE S&P Submitted papers may include up to 13 pages of text and up to 5 pages for references and appendices, totalling no more than 18 pages.

\begin{document}
\pagenumbering{arabic}
\title{{UPPRESSO}: An Unlinkable Privacy-PREserving Single Sign-On System}
\maketitle
\begin{abstract}
Single sign-on (SSO) services
     are widely provided in the Internet by identity providers (IdPs) as the identity management
      and authentication infrastructure.
After being authenticated by the IdP,
    a user is allowed to log into relying parties (RPs) by submitting an \emph{identity proof}
    (i.e., id token of OpenID Connect or SAML assertion).
However,
    SSO introduces the potential leakage of user privacy,
        as (\emph{a}) a curious IdP could track a user's all visits to any RP
            and (\emph{b}) collusive RPs could link the user identity across different RPs,
            to learn the user's detailed activity profile.
%However, the privacy leakage is an obstacle to the users' adoption of SSO,
% as the curious IdP may track at which RPs users log in,
%while collusive RPs could link the user from a common or related identifer(s) issued by the IdP.
Existing privacy-preserving SSO solutions protect the users' activity profiles
    against either the curious IdP or the collusive RPs, but never prevent both of these threats.

In this paper, we propose an SSO system, called \emph{UPRESSO},
     to protect a user's activity profile of RP visits
        from both the curious IdP and the collusive RPs.
In each login process of UPRESSO,
 the IdP that is aware of all users' identities,
         computes the privacy-preserving pseudo-identity ($PID_U$) for a user,
    based on the user's identity and the pseudo-identity ($PID_{RP}$) of the visited RP.
$PID_{RP}$ bound along with $PID_U$ in the identity proof,
   is transformed cooperatively by the user and the RP,
    and then the IdP does not know the visited RPs.
%  and binds $PID_U$ with a transformation of the RP identifier ($PID_{RP}$), without obtaining the real RP identifier.
The visited RP thats obtain a trapdoor from the transformation of $PID_{RP}$,
    is able to use this trapdoor to derive the user's unique account from $PID_U$,
 while a user's accounts are different across the RPs.
The login process of UPRESSO adopts the communication pattern of OpenID Connect, a widely deployed SSO system.
  %  and $PID_{RP}$ is .
% compatible这个词，说得比较勉强；因为不同的人，对于compatible会有不同的理解;
% 至于PRI_{RP}如何放进来，感觉是个次要的事情，不知道单点拿出来说
%UPRESSO is compatible with OpenID Connect, a widely deployed and well analyzed SSO system;
%    where dynamic registration is utilized to make $PID_{RP}$ valid in the IdP.
The analysis demonstrates that UPRESSO protects user privacy well, without any degradation on the security of OpenID Connect.
We have implemented the prototype of UPRESSO and
 the experimental evaluation shows that UPRESSO is efficient and
  it takes only 208 ms for a user to log into an RP.
\end{abstract}
\begin{IEEEkeywords}
Single sign-on, security, privacy. %, trace, linkage
\end{IEEEkeywords}

\input{chap_Compact/introduction.tex}
\input{chap_Compact/background.tex}
\input{chap_Compact/challenges.tex}
\input{chap_Compact/threatmodel.tex}
\input{chap_Compact/protocol.tex}
\input{chap_Compact/analysis.tex}
\input{chap_Compact/implementation.tex}
\input{chap_Compact/evaluation.tex}
\input{chap_Compact/discussion.tex}
\input{chap_Compact/relatedwork.tex}
\input{chap_Compact/conclusion.tex}

\bibliographystyle{IEEEbib}
\bibliography{ref}

\end{document}

%2020.2.6
%introdution 中，讲述IdP和RP合谋，arge IdPs, especially social IdPs like Google and Facebook
%introdution 中，We have implemented a prototype of UPRESSO based on an open-source implementation of OIDC，讲下动态注册。
%3.A 中Receiver designation这个词（binding 和 user确保只发给对应RP）。 integrity和confidentity（HTTPS）放在一起。

%RPID renew---》refresh